---
name: "Charles Taragin"
position: "Principal Economist"
address: "1801 K St NW, Washington, DC 20006"
phone: 734-276-6812
www: "luciu5.github.io"
linkedin: "charles-taragin-b950a668"
email: "ctaragin@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
header-includes:
  - \definecolor{awesome-teal}{HTML}{0f766e}
  - \colorlet{awesome}{awesome-teal}
  - \geometry{left=2.2cm, top=2.2cm, right=2.2cm, bottom=2.2cm, footskip=.6cm}
  - \renewcommand{\acvHeaderAfterNameSkip}{1.2mm}
  - \renewcommand{\acvHeaderAfterPositionSkip}{1.0mm}
  - \renewcommand{\acvHeaderAfterAddressSkip}{0.8mm}
  - \renewcommand{\acvHeaderAfterSocialSkip}{8.0mm}
  - \renewcommand{\acvSectionTopSkip}{5.8mm}
  - \renewcommand{\acvSectionContentTopSkip}{4.0mm}
  - \renewenvironment{cvitems}{\vspace{0.1mm}\begin{justify}\begin{itemize}[leftmargin=2.5ex, nosep, itemsep=3.8pt]\setlength{\parskip}{1.5pt}\renewcommand{\labelitemi}{\bullet}}{\end{itemize}\end{justify}\vspace{0.4mm}}
  - \let\oldcventry\cventry
  - \renewcommand*{\cventry}[5]{\oldcventry{#1}{#2}{#3}{#4}{#5}\vspace{0.35mm}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

education <- data.frame(degree=c("PhD","Masters","Masters","Bachelors"),
                                 type=c("Economics","Economics","Public Policy", "Economics"),
                                 inst=rep(c("University of Michigan","University of Chicago"),each=2),
                                 year=c(2007,2004,2000,1999)
                       )

experience_doj <- data.frame(
  what="Economist",
  when="September 2007 - May 2019",                       
  with="Antitrust Division, U.S. Department of Justice",
  where="Washington DC",
  why=c(
    "Served as an economist on major merger investigations and litigations, including Anthem / Cigna (health insurance), American Airlines / US Airways (airlines), National CineMedia / Screenvision (cinema advertising), Twin America ('hop-on, hop-off' tour buses), Standard Parking / Central Parking (parking facilities), and radio station advertising mergers.",
    "Modeled market-wide pricing and welfare impacts of Washer and Steel tariffs and import quotas proposed during the first Trump administration.",
    "Authored core code and mathematical frameworks (in R and Stata) for horizontal merger, tariff, and quota simulations used frequently in Antitrust Division investigations.",
    "Designed and coded interactive web interfaces for merger and tariff simulation tools.",
    "Designed and maintained massive databases (exceeding 10 TB) to support complex antitrust investigations and federal court litigation."
  )
)

experience_ftc <- data.frame(
  what="Economist",
  when="June 2019 - September 2022",                       
  with="Federal Trade Commission",
  where="Washington DC",
  why=c(
    "Collaborated with attorneys to model and quantify competitive effects in merger investigations, including vertical integration in the NVIDIA / ARM semiconductor merger (FTC challenge)."
  )
)

experience_frb <- data.frame(
  what="Principal Economist",
  when="September 2022 - present",                       
  with="Federal Reserve Board",
  where="Washington DC",
  why=c(
    "Lead the economic analysis of bank mergers and divestitures, including the high-profile Capital One / Discover merger (joint Board and DOJ investigation)."
  )
)

presentations <- data.frame(what = c("Federal Trade Commission","DC IO Day","International Industrial Organization Conference","Federal Trade Commission","International Competition Network","International Industrial Organization Conference","Federal Communication Commission","U.S. Department of Justice"),
                            when=   c("11/2025","5/2019","4/2019","6/2018, 7/2018","2018","2018","8/2018, 2013","2012, 2017")
)

service <- data.frame(what=c("Acting Advisor to Commissioner Noah Phillips", "US DoJ/KFTC Knowledge Exchange Program","Algorithmic Document Review","R Training"),
                      when=c("2020", "2018","2017","2012 - present"),
                      why= c("Served as Acting Advisor to Commissioner Noah Phillips for three months.",
                             "Organized, co-authored and co-taught a 3 day training program for new economists at the Korean Free Trade Commission (KFTC). The purpose of this program was to train KFTC economists in how to analyze horizontal mergers.",
                             "Trained a series of machine learning classifiers to predict if a document is pertinent to an investigation. Once these models have been fully tested, they will greatly reduce the time needed to review the massive amount of documents received by the Antritrust Division.",
                             "Authored and co-taught a series of short courses for Economists  and Research Analysts on R. Covered topics included: data analysis, plotting, regression analysis, mapping, interfacing with databases, and antitrust analysis.")
                      )
awards <- data.frame(when=c(2025, 2019, 2017:2014, 2010),
                     what=c("Team Special Achievement Award for work on Capital One/Discover Merger",
                            "EAG Management Award For Positive Externality",
                            "Team Award for work on Anthem/Cigna litigation",
                            "EAG Management Award For Extraordinary Achievement",
                            "Team Award for work on National Cinemedia/Screenvision litigation",
                            "Team Award for work on American/US Airways litigation",
                            "EAG Management Award For Pushing Frontiers"
                            )
                     )

```
## Executive Summary
Antitrust and competition-policy economist with over 15 years of experience leading high-profile merger investigations at the Federal Reserve Board, Federal Trade Commission, and Department of Justice. Specialist in merger review under uncertainty, horizontal and vertical merger simulation, spatial market definition, and industrial organization. Developer of standard open-source R packages for antitrust simulation and policy analysis.

## Experience
```{r experience}

detailed_entries(experience_frb,
                  what = what,
                 when = when,
                 with = with,
                 where = where,
                 why = why)
detailed_entries(experience_ftc,
                  what = what,
                 when = when,
                 with = with,
                 where = where,
                 why = why)

detailed_entries(experience_doj,
                  what = what,
                 when = when,
                 with = with,
                 where = where,
                 why = why)
```


## Education
```{r education}
detailed_entries(education,
                 what = degree,
                 when = year,
                 with = type,
                 where = inst)
```

## Publications
```{r publications}
bibliography_entries("published.bib")
```

## Under Review
```{r underreview}
bibliography_entries("underreview.bib")
```

## In Progress
```{r progress}
bibliography_entries("progress.bib")
```

## R Software Packages
```{r rpkgs}
rpkgs <- data.frame(
  package = c("antitrust", "trade", "competitiontoolbox"),
  title = c("Tools for Antitrust Practitioners", "Tools for Trade Policy Analysis", "Graphical User Interface for Antitrust and Trade Packages"),
  description = c("A collection of tools for antitrust practitioners, including merger simulation models, market definition, and equilibrium pricing. Calibrates demand parameters and simulates mergers under various differentiated products demand systems including logit, nested logit, ces, and aids.",
                  "A collection of tools for trade policy analysis. Provides trade policy practitioners with a tractable framework for simulating the effects of tariffs, quotas, and other trade policy measures on market outcomes.",
                  "A graphical user interface for the antitrust and trade R packages. Provides an interactive interface for conducting merger simulations, market definition analysis, and trade policy analysis without requiring R programming knowledge.")
)

detailed_entries(rpkgs,
                 what = package,
                 why = description
)
```

## Presentations
```{r presentations}
detailed_entries(presentations,
                 what = what,
                 when = when
                 )
```


## Service
```{r service}
detailed_entries(service,
                  what = what,
                 when = when,
                 why = why)
```


## Awards
```{r awards}
detailed_entries(awards,
                  what = what,
                 when = when)
```

## Technical Skills & Competencies
```{r skills}
skills_data <- data.frame(
  class = c("Methods", "Programming", "Databases"),
  skills = c("Merger Simulation, Structural Econometrics, Spatial Market Definition, Bargaining Models",
             "R (Core Package Developer), Python, C++, Java",
             "PostgreSQL, DuckDB, SQLite, PostGIS, MySQL")
)

detailed_entries(skills_data,
                  what = class,
                 why = skills)
```

